---
title: "MISR Data Modelling"
author: "Joey Hotz"
date: "Last Updated: September 27, 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/johot/Desktop/Joey's Files/Work/NSERC 2022/PM25-Research")

library(tidyverse)
library(data.table)

```

## Reading Data

First, we will read in the MISR datasets which have been matched to the AQS and CSN datasets. These data were matched spatially by considering every AQS/CSN data collection site within a 2.2 km radius of a MISR data pixel, and these matches were further filtered by matching these observations based on the dates when they were recorded.
```{r}
MISR_AQS <- read_csv(paste0(getwd(), "/Data/MISR/MISR_merged_data/MISR_AQS_Matched.csv"), show_col_types = FALSE)
MISR_CSN <- read_csv(paste0(getwd(), "/Data/MISR/MISR_merged_data/MISR_CSN_Matched.csv"), show_col_types = FALSE)
```

## Exploratory Data Analysis

## Charts and Graphs

Next, we will create some charts and plots of the matched MISR data, to get visual representations of the data which we have collected.

First, we will create a "correlation heatmap" to visually depict the correlations between the 74 AOD mixtures which were collected in the MISR data.

